An Analysis of the SPDY Protocol as a Candidate for HTTP/2.0

### 2012-12-19 paper/paper.tex
Rewrite some of the SPDY asset introduction

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Asset Characterization}
\label{sec:assets}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{SPDY Combination Strategy}
SPDY's most complex new feature is the ability to multiplex requests for assets
over a single TCP connection. In this way, a web page's assets can benefit from
a warmed-up TCP connection which is not subject to the TCP slow start
algorithm. Since SPDY is currently built atop SSL, SPDY can only combine assets
with a mutually-agreeable SSL certificate. The assets will be combined into
separate streams over the same TCP connection, thus ideally obtaining complete
utilization of the connection and the benefit from TCP's eventual discovery of
an accurate congestion window.

In order to measure the efficiency of SPDY's asset combination, we must
determine the benefit of combining assets. The authors of SPDY claim that the
main benefit from asset combination is the reduction of network connections
required~\cite{spdy-whitepaper}. Although the HTTP/1.1 specification allows for
up to two simultaneous connections to servers, modern browsers willfully
violate it in service of page load speed and will happily open up to six
connections to each host. Websites have also been pushing the limits by
creating semantically equivalent hostnames (i.e. assets1.example.com,
assets2.example.com, etc.) for different asset servers so browsers will open
six connections to each. Thus, browsers may wind up opening hundreds of
connections immediately upon loading a page.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Asset Characterization}
\label{sec:assets}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{SPDY Combination Strategy}
SPDY's most complex new feature is the ability to multiplex requests for assets
over a single TCP connection. In this way, a web page's assets can benefit from
a warmed-up TCP connection which has passed the beginning of the TCP slow start
algorithm. Since SPDY is currently built atop SSL, SPDY can only combine assets
with a mutually-agreeable SSL certificate. The assets will be combined into
separate, interleaved streams over the same TCP connection, thus ideally
obtaining complete utilization of the connection and the benefit from TCP's
eventual discovery of an accurate congestion window.

In order to measure the efficiency of SPDY's asset combination, we must
determine what metric benefits from combining assets. The authors of SPDY claim
that the main benefit from asset combination is the reduction of network
connections required~\cite{spdy-whitepaper}.

Although the HTTP/1.1 specification allows for up to two simultaneous
connections to servers, modern browsers willfully violate it in service of page
load speed and will happily open up to six connections to each host. Websites
have also been pushing the limits by creating semantically equivalent hostnames
for asset servers (i.e. assets1.example.com, assets2.example.com, etc.) so
browsers will open six connections to each. Thus, browsers may wind up opening
hundreds of connections immediately upon loading a page -- thus dishonoring the
intent of TCP slow start.
